Competing Bandits: The Perils of Exploration under Competition

### 2018-08-30 paper/content/perf_in_iso.tex
Barely started.

\section{Performance in Isolation}\label{section:4}

We evaluate the performance of the different learning algorithms on the bandit priors we consider in isolation. There are two reasons why this is important to consider. First, we want to confirm that the reputation ordering of the algorithms is what we would expect according to the multi-armed bandit literature where, according to the mean reputation, $\TS > \DEG > DG$ for sufficiently large $t$. Second, we want to better understand what statistics of the priors we can look at in isolation in order to help us predict and understand what to expect in the competition game.

>>>>

\section{Algorithms' Performance in Isolation}\label{section:4}

We start with a pilot experiment in which we investigate each algorithm's performance "in isolation": in a stand-alone bandit problem without the competition.

STOPPED HERE.

First, we want to confirm that the reputation ordering of the algorithms is what we would expect according to the multi-armed bandit literature where, according to the mean reputation, $\TS > \DEG > DG$ for sufficiently large $t$. Second, we want to better understand what statistics of the priors we can look at in isolation in order to help us predict and understand what to expect in the competition game.
